Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-11-18 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
Fixes error

This is in part due to the fact that the presence of nodes is not
constant, as shown in Figure \cite{fig:ips:rastrigin}, which plots the
number of unique IPs participating in the experiment per minute (left)
and hour (right). The two graphs have the same shape which matches
also the speed in which fitness is decreased in Figure
\ref{fig:puts:rastrigin}. At the beginning there are very few or only
one, but later one there ar peaks of almost 30 unique machine a
minute; these peaks appear again when new announcements are made in
Twitter or any other social networks, to go down to a few remaining
nodes later on. It is interesting to note that, at the most, more than
100 unique nodes were participating in the experiment during one hour;
also that there are sustained peaks during a day of 6-7 computers
every minute. This is due to the fact that the computation is
asynchronous, but also to the fact that different computers stay in
the simulation for a different period of time. This period has been
plotted in Figure \ref{fig:fit:rastrigin}, that plots the number of
{\tt PUT}s per node, ranked by number, along with a fit to the two
distributions we have used before, GEV and Weibull; the parameters of
this fit are shown in Table \ref{tab:puts:ww:f15}. Unlike the previous
experiments, in which GEV fit was relatively good, in this case it is
quite obviously not. However, the fit to the Weibull distribution,
shown at the left of the image, is relatively good. As should be
expected, the shape and scale are different to the one in the previous
experiments with the Trap function, however, the shape is quite
similar (0.40 vs 0.69), being in both cases less than one, which
indicates a decreasing distribution of the same kind. In fact, the
difference in the scale parameter indicates that the difference
between the time devoted by a volunteer and the next is bigger in this
case. This is probably due to the fact that the duration of the
experiment is bigger, allowing for bigger differences in
behavior. While the first in the Trap function might have devoted a
few minutes and the second a few seconds less, the difference between
the first and second in this experiment might be in the scale of
hours.

>>>>

This is in part due to the fact that the presence of nodes is not
constant, as shown in Figure \ref{fig:ips:rastrigin}, which plots the
number of unique IPs participating in the experiment per minute (left)
and hour (right). The two graphs have the same shape which matches
also the speed in which fitness is decreased in Figure
\ref{fig:puts:rastrigin}. At the beginning there are very few or only
one, but later one there ar peaks of almost 30 unique machine a
minute; these peaks appear again when new announcements are made in
Twitter or any other social networks, to go down to a few remaining
nodes later on. It is interesting to note that, at the most, more than
100 unique nodes were participating in the experiment during one hour;
also that there are sustained peaks during a day of 6-7 computers
every minute. This is due to the fact that the computation is
asynchronous, but also to the fact that different computers stay in
the simulation for a different period of time. This period has been
plotted in Figure \ref{fig:fit:rastrigin}, that plots the number of
{\tt PUT}s per node, ranked by number, along with a fit to the two
distributions we have used before, GEV and Weibull; the parameters of
this fit are shown in Table \ref{tab:puts:ww:f15}. Unlike the previous
experiments, in which GEV fit was relatively good, in this case it is
quite obviously not. However, the fit to the Weibull distribution,
shown at the left of the image, is relatively good. As should be
expected, the shape and scale are different to the one in the previous
experiments with the Trap function, however, the shape is quite
similar (0.40 vs 0.69), being in both cases less than one, which
indicates a decreasing distribution of the same kind. In fact, the
difference in the scale parameter indicates that the difference
between the time devoted by a volunteer and the next is bigger in this
case. This is probably due to the fact that the duration of the
experiment is bigger, allowing for bigger differences in
behavior. While the first in the Trap function might have devoted a
few minutes and the second a few seconds less, the difference between
the first and second in this experiment might be in the scale of
hours.
